Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-06-18 sas2015/content/example.tex
applying Frank's comments
fixing appendix sentence

\subsection{Occurrences of Correlated Calls}\label{sec:occur}\vspace{-.5mm}
How often do correlated calls occur in practice? To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occur in programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework~\cite{fink2012wala}.
Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis. The results are shown in Table~\ref{tab:dacapostat} in the Appendix.

@@

However, the implementation of \code{TraversableOnce.toArray} is actually correct because the above
code is guarded with a test: \code{if (this.isTraversableAgain) ...}
%\inputMintedNoLNs{scala}{isTraversable.scala}
When the \code{isTraversableAgain} method returns false, as it does for
an iterator, the \code{toArray} method uses a different
(less efficient) implementation. The bug report would therefore be a false positive. 
The \code{isTraversableAgain} method is easy to analyze: it returns the constant
true in a collection and the constant false in an iterator. However, in order
to eliminate the false positive bug report, an analysis would need to rule out infeasible
paths using correlated calls. Specifically, the following path triggers the bug, but
is infeasible: first, call \code{isTraversableAgain} on a collection, returning
true, then call \code{size} and \code{copyToArray} on an iterator. Our correlated
calls analysis could determine that this path is infeasible because it calls the
collection version of \code{isTraversableAgain} but the iterator versions of
\code{size} and \code{copyToArray}.
The relevant code from \textsf{TraversableOnce} and other related traits is shown
in Figure~\ref{fig:traversableonce} in the Appendix.

>>>>

\subsection{Occurrences of Correlated Calls}\label{sec:occur}\vspace{-.5mm}
How often do correlated calls occur in practice? To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occur in programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework~\cite{fink2012wala}.
Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis. The results are shown in\techreport{ Table~\ref{tab:dacapostat} in } the~\reportOrAppendix.

@@

However, the implementation of \code{TraversableOnce.toArray} is actually correct because the above
code is guarded with a test: \code{if (this.isTraversableAgain) ...}
%\inputMintedNoLNs{scala}{isTraversable.scala}
When the \code{isTraversableAgain} method returns false, as it does for
an iterator, the \code{toArray} method uses a different
(less efficient) implementation. The bug report would therefore be a false positive. 
The \code{isTraversableAgain} method is easy to analyze: it returns the constant
true in a collection and the constant false in an iterator. However, in order
to eliminate the false positive bug report, an analysis would need to rule out infeasible
paths using correlated calls. Specifically, the following path triggers the bug, but
is infeasible: first, call \code{isTraversableAgain} on a collection, returning
true, then call \code{size} and \code{copyToArray} on an iterator. Our correlated
calls analysis could determine that this path is infeasible because it calls the
collection version of \code{isTraversableAgain} but the iterator versions of
\code{size} and \code{copyToArray}.
The relevant code from \textsf{TraversableOnce} and other related traits is shown
\techreport{in Figure~\ref{fig:traversableonce} }in the \reportOrAppendix.
